Analyzing the Impact of Social Attributes on Commit Integration Success

### 2017-03-27 Paper/MSRChallenge2017.tex
todo

F-score is a correlation\todo{this is not true; please correct} of these two values. We can see that all these measures increase when we add social data into the feature space, making the prediction more reliable. Besides this, the mean absolute error
decreases in both cases, which provides further evidences that social factors
are important when predicting build success.

>>>>

F-score is a correlation\todo{this is not true; please correct.  Also, we really
don't have the space to include precision/recall formulae, given that they're
well-known; correct your understanding, then delete this comment and the formulae} of these two values. We can see that all these measures increase when we add social data into the feature space, making the prediction more reliable. Besides this, the mean absolute error
decreases in both cases, which provides further evidences that social factors
are important when predicting build success.
